---
title: "Assignment_1"
author: "Akhila SriMedarametla"
date: "23/09/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Problem 


**a. Define the decision variables**

The decision variables  = Number of units of the new product produced on each plant(regardless of its size) 


  $X_i$ = means the number of units produced on each plant, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 
3).

    L, M, and S = means the product's size, where L = large, M = medium, and S = small.

    $X_iL$ = number of large items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

    $X_iM$ = number of medium items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

    $X_iS$ = number of small items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).



**b. Formulate a linear programming model for this problem.**

Let 

    $X_iL$ = number of large items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

    $X_iM$ = number of medium items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

    $X_iS$ = number of small items produced on on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).


Maximize profit 

    $Z= 420 \ (X_1L + X_2L + X_3L) + 360 \ (X_1M + X_2M + X_3M) + 300 / (X_1S + X_2S + X_3S)$


Constraints:

  Total number of size’s units produced regardless the plant:

    $L = X_1L + X_2L + X_3L$

    $M = X_1M + X_2M + X_3M$

    $S = X_1S + X_2S + X_3S$

  Production capacity per unit by plant each day:

    Plant 1 = $X_1L + X_1M + X_1S \ 750$

    Plant 2 = $X_2L + X_2M + X_2S \ 900$

    Plant 3 = $X_3L + X_3M + X_3S \ 450$

  Storage capacity per unit by plant each day:

    Plant 1 = $20 X_1L + 15 X_1M + 12 X_1S \13000$

    Plant 2 = $20 X_2L + 15 X_2M + 12 X_2S \ 12000$

    Plant 3 = $20 X_3L + 15 X_3M + 12 X_3S \ 5000$

  Sales forecast per day:

    $L = X_1L + X_2L + X_3L \ 900$

    $M = X_1M + X_2M + X_3M \ 1200$

    $S = X_1S + X_2S + X_3S \ 750$

  The plants should use the same percentage of their excess capacity to produce the new product. 


    $\dfrac {X_1L + X_1M + X_1S} {750}$ = $\dfrac {X_2L + X_2M + X_2S} {900}$ = $\dfrac {X_3L + X_3M + X_3S} {450}$


      It can be simplified as:

          a) $900 (X_1L + X_1M + X_1S) - 750 (X_2L + X_2M + X_2S) = 0$

          b) $450 (X_2L + X_2M + X_2S) - 900 (X_3L + X_3M + X_3S) = 0$

          c) $450 (X_1L + X_1M + X_1S) - 750 (X_3L + X_3M + X_3S) = 0$

  All values must be greater or equal to zero

    $L, M,$ and $S \ 0$

    $X_iL, X_iM,$ and $X_iS \ 0$


```{r}
# Import the lpSolve package. 
library(lpSolve)
# Set coefficients for objective function.
my_obfunct <- c(420, 420, 420,
                360, 360, 360,
                300, 300, 300)
# Set the left hand side of the problem's constraints.
my_lefconst <- matrix(c(1, 1,1 ,0, 0, 0,0, 0, 0,
                        0,0, 0,1, 1, 1, 0, 0, 0,
                        0, 0, 0, 0, 0, 0, 1, 1, 1,
                        20, 15, 12, 0, 0, 0, 0, 0,0,
                        0, 0, 0, 20, 15, 12, 0, 0, 0,
                        0, 0, 0, 0, 0, 0, 20, 15, 12,
                        1, 0, 0, 1, 0, 0, 1, 0, 0,
                        0, 1, 0, 0, 1, 0, 0, 1, 0,
                        0, 0, 1, 0, 0, 1, 0, 0, 1,
                        900, 900, 900, -750, -750, -750, 0, 0, 0,
                        0, 0, 0, 450, 450, 450, -900, -900, -900,
                        450, 450, 450, 0, 0, 0, -750, -750, -750), nrow = 12, byrow = TRUE)

# Set the right hand side of the problem's constraints.
my_rigconst <- c(750,
                 900,
                 450,
                 13000,
                 12000,
                 5000,
                 900,
                 1200,
                 750,
                 0,
                 0,
                 0)
# Set the unequality signs
my_signs <- c("<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "=",
              "=",
              "=")
# Set up the final lp problem

lp("max", my_obfunct, my_lefconst, my_signs, my_rigconst)
# To get the soluction of the lp problem
lp("max", my_obfunct, my_lefconst, my_signs, my_rigconst)$solution
```



