---
title: "Assignment_5"
author: "Akhila Sri Medarametla"
date: "16/04/2022"
output:
  pdf_document: default
  word_document: default
---

```{r}
library(readr)
Cereals <- read_csv("C:/Users/Dell/Desktop/Cereals.csv")
View(Cereals)



```
# Removing missing values

```{r}

head(Cereals)
null_model <- is.null(Cereals)
null_model

n_a <- is.na(Cereals)
n_a

Cereals_new <- data.frame(Cereals[,4:16])

 
Cereals_rmv<- na.omit(Cereals_new)
Cereals_rmv
z <- is.na(Cereals_rmv)
z



````
# Nomalizing data
```{r}

 Cereals_norm <- scale(Cereals_rmv)
 Cereals_norm


```
# using euclidean distance measure to normalized data
```{r}


Eucli_distance <- dist(Cereals_norm, method = "euclidean")

```
# checking number of cluster using complete linkage
```{r}
hierarchical_complete <- hclust(Eucli_distance, method = "complete")
plot(hierarchical_complete )
round(hierarchical_complete$height, 3)
plot(hierarchical_complete)



```



#  Using Agnes for single linkage, complete linkage, average linkage, and Ward.
```{r}

library("cluster")
single_cluster <- agnes(Cereals_norm, method = "single")
complete_cluster <- agnes(Cereals_norm, method = "complete")
average_cluster <- agnes(Cereals_norm, method = "average")
ward_cluster <- agnes(Cereals_norm, method = "ward")



```


# comparing  agglomerative coefficients 

```{r}
print(single_cluster$ac)

print(complete_cluster$ac)

print(average_cluster$ac)

print(ward_cluster$ac)


```
# Ward cluster has the highest agglomerative coefficient i.e 0.9046. plot using ward method

```{r}

hierarchical_ward <- hclust(Eucli_distance, method = "ward")
plot(hierarchical_ward)

```

# by observing ward cluster agglomerative coefficient and dendogram we can choose k=5 cluster
```{r}
plot(ward_cluster)
rect.hclust(ward_cluster,k = 5, border = "Orange")

pltree(ward_cluster, cex = 0.6, hang = -1, main = "Dendrogram of agnes-Ward")
```

# finding the group of healthy cereals
```{r}
clus_ward <- hclust(Eucli_distance, method = "ward.D2" )
group <- cutree(clus_ward, k = 5)
table(group)
library("factoextra")
fviz_cluster(list(data= Cereals_norm,cluster = group))

```

# diving groups for finding healthy cereals 

```{r}
healthy_cluster <- cbind(Cereals_rmv,group)
healthy_cluster
healthy_cluster[healthy_cluster$group==1,]
healthy_cluster[healthy_cluster$group==2,]
healthy_cluster[healthy_cluster$group==3,]
healthy_cluster[healthy_cluster$group==4,]
healthy_cluster[healthy_cluster$group==5,]


```

# finding the cluster with healthy cereals
```{r}


mean(healthy_cluster[healthy_cluster$group==1,"rating"])

mean(healthy_cluster[healthy_cluster$group==2,"rating"])

mean(healthy_cluster[healthy_cluster$group==3,"rating"])

mean(healthy_cluster[healthy_cluster$group==4,"rating"])

mean(healthy_cluster[healthy_cluster$group==5,"rating"])
```

# group 1 has the highest mean which means cluster 1 has healthy diet